---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data <- read.csv(unz("activity.zip", "activity.csv"))
steps_by_date <- aggregate(steps ~ date, data, sum)
```

## What is mean total number of steps taken per day?
```{r}
hist(steps_by_date$steps, xlab="Steps", main="Steps by Date")
mean_steps_by_date <- mean(steps_by_date$steps)
median_steps_by_date <- median(steps_by_date$steps)
```
Mean steps taken per day are `r mean_steps_by_date`

Median steps taken per day are `r median_steps_by_date`

## What is the average daily activity pattern?

```{r}
avg_steps_by_interval <- aggregate(steps ~ interval, data, mean)
plot(avg_steps_by_interval, type='l')
max_interval <- avg_steps_by_interval[which.max(avg_steps_by_interval$steps),]$interval
```

The time interval `r max_interval` contains the maximum number of steps

## Imputing missing values

```{r}
nmissing <- sum(is.na(data$steps))
library(plyr)
data_imputed <- ddply(data, 
      .(interval), 
      transform, 
      steps=ifelse(is.na(steps), median(steps, na.rm=TRUE), steps))
```

There are `r nmissing` missing values in the dataset

```{r}
steps_by_date <- aggregate(steps ~ date, data_imputed, sum)
hist(steps_by_date$steps, xlab="Steps", main="Steps by Date")
mean_steps_by_date <- mean(steps_by_date$steps)
median_steps_by_date <- median(steps_by_date$steps)
```

Mean steps taken per day are `r mean_steps_by_date`
Median steps taken per day are `r median_steps_by_date`

## Are there differences in activity patterns between weekdays and weekends?
